\mcvsection{Schulische \& Akademische Ausbildung}{School \& Academic Education}

\begin{cventries}

    %#1/4 What #2/5 institue #3/6 where #7 when #8 list
	\mcventry{Promotion, Dr. rer. nat. (Informatik)}{Julius-Maximilians-Universität}{Würzburg, Deutschland}%
	{Doctoral candidate, Dr. rer. nat. (Computer Science)}{University of Würzburg}{Würzburg, Germany}%
	{\fromto{}{10}{2016}{}{12}{2020}}%
	{
		\begin{cvitems} % Description(s) bullet points
			\item {\textbf{Dissertation} ``Automated Hybrid Time Series Forecasting: Design, Benchmarking, and Use Cases''}
			\item {\textbf{\twonames{Betreuer}{Advisor}} Prof. Dr. Samuel Kounev}
			\item {\textbf{\twonames{Bewertung}{Grade}} Summa cum laude (\twonames{1,0}{1.0}) --- \entrydatestyle{Disputation \dategenerator{22}{12}{2020}}}
		\end{cvitems}
	}

    %#1/4 What #2/5 institue #3/6 where #7 when #8 list
	\mcventry{Masterstudium, M.Sc. (Informatik)}{Julius-Maximilians-Universität}{Würzburg, Deutschland}%
	{Master of Science in Computer Science}{University of Würzburg}{Würzburg, Germany}%
	{\fromto{}{10}{2014}{}{9}{2016}}%
    {
        %\begin{cvitems}
    	%		\item {\textbf{Thesis} ``Design and Evaluation of a Proactive, Application-Aware Elasticity Mechanism''}
    	%		\item {\textbf{\twonames{Abschlussnote}{Final grade}} \twonames{1,3}{1.3}}
    	%\end{cvitems}
	}

	%#1/4 What #2/5 institue #3/6 where #7 when #8 list
	\mcventry{Auslandssemester (Erasmus-Programm)}{Blekinge Institute of Technology}{Karlskrona, Schweden}%
	{Semester abroad (Erasmus program)}{Blekinge Institute of Technology}{Karlskrona, Sweden}%
    {\fromto{}{8}{2015}{}{1}{2016}}%
    {}

    %#1/4 What #2/5 institue #3/6 where #7 when #8 list
	\mcventry{Bachelorstudium, B.Sc. (Informatik)}{Julius-Maximilians-Universität}{Würzburg, Deutschland}%
	{Bachelor of Science in Computer Science}{University of Würzburg}{Würzburg, Germany}%
    {\fromto{}{10}{2012}{}{10}{2014}}%
    {
        %\begin{cvitems}
    	%		\item {\textbf{Thesis} ``On Algorithms for Socially-Aware Prediction of Individual Content Requests''}
    	%		\item {\textbf{\twonames{Abschlussnote}{Final grade}} \twonames{1,6}{1.6}}
    	%\end{cvitems}
	}



\end{cventries}